---
title: "JW-Workspace2"
author: "Justin Weltz"
date: "2/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(corrgram)
```

```{r}
load("dat.Rdata")
#Questions
data_B15 <- dat99 %>% select(starts_with("B15"))
```

Data Preprocessing
```{r Variable without imputations}
data <- dat99 %>% mutate(Ind_Comment = as.numeric(COMMENTS == 1)) #original 1:yes; 2:no
data <- data %>% mutate(Gender = SEX) #0:F; 1:M
data <- data %>% mutate(Age_Group = as.numeric(AGEGROUP == 1)) #1:<21; 0: >=21
data <- data %>% mutate(Alc_Problem = as.numeric(B1 != 4)) #1: is problem; 0: not a problem
data <- data %>% mutate(AP_all = as.numeric(B2 == 1)) %>%
                 mutate(AP_stu = as.numeric(B2 == 2)) %>%
                 mutate(AP_all21 = as.numeric(B2 == 3)) %>%
                 mutate(AP_stu21 = as.numeric(B2 == 4)) %>%
                 mutate(AP_no = as.numeric(B2 == 5)) %>%
                 mutate(AP_notknow = as.numeric(B2 == 6))
data <- data %>% mutate(Enforce_Pol = as.numeric(B3 == 1 | B3 == 2 | B3 == 3)) #1: enforeced
data <- data %>% mutate(Agree_Pol = as.numeric(B4 == 1 | B4 == 2)) #1: agree
data <- data %>% mutate(Change_Pol = as.numeric(B5 == 2 | B5 == 3)) #1: change
data <- data %>% mutate(Min_Drink_Age = as.numeric(B13 != 5 )) #1: <21
data <- data %>% mutate(Advice = D4) %>% mutate(Complaint = D5) %>% mutate(Perception = D3B/D3A)
```

```{r Variable with imputations (survey set up)}
# Drink Occasions
data <- data %>% mutate(Drink_Occ = ifelse(is.na(C9), ifelse(C8 == 1 | C8 == 2 | C8 == 3,
                                                      1, C9), C9))
# Drink numbers
data <- data %>% mutate(Drink_Num = ifelse(is.na(C10), ifelse(C8 == 1 | C8 == 2 | 
                                                                C8 == 3,0, C10), C10))
```

Final Data
```{r}
DRINKCAT <- data$DRINKCAT
final_data <- cbind(data_B15, DRINKCAT, data[,456:ncol(data)])
```

Treatment for NA's -> Remove (could try non-parametric imputation)
```{r}
na_check <- is.na(final_data)
na_row <- apply(na_check,1,sum)
final_data <- final_data[na_row==0,]
```

Build first part of SEM to get residuals:
```{r}
require(lavaan)
HS.model <- ' #Measurement Model 
              personal  =~ B15A + B15D + B15G + B15H + B15I + B15J 
              communal =~ B15B + B15C + B15E + B15F
              #Regressions
              personal ~ Drink_Num + Drink_Occ + Advice + Complaint + Perception + Enforce_Pol
              communal ~ Drink_Num + Drink_Occ + Advice + Complaint + Perception + Enforce_Pol'

fit <- sem(HS.model, data=final_data, ordered = c("B15A", "B15B","B15C","B15D","B15E","B15F", "B15G", "B15H", "B15I", "B15J"))
summary(fit)
```

Obtain the residuals of B15's from SEM (store it as "residual2"):
```{r}
# Fitted values of survey responses
ov_pred <- lavPredict(fit, type = "ov")
ov_pred <- data.frame(ov_pred)

# Observed values
obs_data <- final_data

# Reorder the columns to compute residuals
ov_pred_B15 <- cbind(ov_pred$B15A, ov_pred$B15B, ov_pred$B15C,
                     ov_pred$B15D, ov_pred$B15E, ov_pred$B15F,
                     ov_pred$B15G, ov_pred$B15H, ov_pred$B15I,
                     ov_pred$B15J)
obs_B15 <- cbind(obs_data$B15A, obs_data$B15B, obs_data$B15C,
                 obs_data$B15D, obs_data$B15E, obs_data$B15F,
                 obs_data$B15G, obs_data$B15H, obs_data$B15I,
                 obs_data$B15J)

# Compute residuals and rename the columns
residual2 <- data.frame((obs_B15 - ov_pred_B15)^2)
names(residual2) <- c("B15A_Res2","B15B_Res2","B15C_Res2",
                      "B15D_Res2","B15E_Res2","B15F_Res2",
                      "B15G_Res2","B15H_Res2","B15I_Res2","B15J_Res2")
```

Now, fit the second part of SEM:
Ideally, this is the regression model, but it has 2 problems: 
1. not converge. 
2. sigma matrix is not positive definite (probably due to 6 variables for B2)

engagement ~ Gender + Age_Group + DRINKCAT + Alc_Problem +
             AP_all + AP_stu + AP_all21 + AP_stu21 + AP_no + AP_notknow +
             Enforce_Pol + Agree_Pol + Change_Pol + Min_Drink_Age +
             Drink_Occ + Drink_Num + Advice + Complaint + Perception
             
It's thus simplified as follows: note the Drink_Occ and Drink_Num are removed for convergence as well. We are using DRINKCAT to measure the alcohol level for each respondent:
```{r}
# Combine final and residuals, drop original responses (B15A-B15J):
data_w_res <- cbind(final_data, residual2)
data_w_res <- data_w_res[,11:ncol(data_w_res)]

SEM.model <- ' #Measurement Model 
                engagement  =~ B15A_Res2 + B15B_Res2 + B15C_Res2 + B15D_Res2 +
                               B15E_Res2 + B15F_Res2 + B15G_Res2 + B15H_Res2 +
                               B15I_Res2 + B15J_Res2 + Ind_Comment
               #Regressions
                engagement ~ Gender + DRINKCAT + Alc_Problem + 
                             Enforce_Pol + Agree_Pol + Change_Pol + Min_Drink_Age +
                             Advice + Complaint + Perception
                             '

fit <- sem(SEM.model, data=data_w_res)
summary(fit)
```

Visualizations:
```{r}
library(semPlot)
semPaths(fit)
```

