---
title: "JW Workspace"
author: "Justin Weltz"
date: "2/7/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(dplyr)
require(corrgram)
load("dat.Rdata")
```

Useful Functions
```{r}
colvar <- function(x){
  
  rowSums((x - rowMeans(x))^2)/(dim(x)[2]-1)
}

find_colvar <- function(str){
  x <- dat99 %>% select(starts_with(str))
  colvar(x)
}
```

Extract Important Predictor Variables - Importance and Support (Variance)
```{r}
predictor_vars <- c("A12", "B15", "C20", "C22")
pred_data <- matrix(NA, dim(dat99)[1], length(predictor_vars))

for (i in 1:length(predictor_vars)){
  pred_data[,i]<- find_colvar(predictor_vars[i])
}
pred_data <- data.frame(pred_data)
names(pred_data) <- c("A12_var", "B15_var", "C20_var", "C22_var")
#View(pred_data)

#corrgram(pred_data)
```

Preliminary Logistic Regression of whether or not a student leaves comments on indicators of survey engagement
```{r}
data <- dat99 %>% mutate(new_comment = COMMENTS == 1)
comments<- as.numeric(data$new_comment)
model_data <-cbind(comments, pred_data)
model <- glm(data= model_data, comments~. , family = "binomial")
plot(model)
summary(model)
corrgram(model_data)
```
Expanded Predictor Class - Importance, Support, Like (Variance)
```{r}
predictor_vars <- c("A12", "B15", "C20", "C22", "B9", "B12", "G9")
pred_data <- matrix(NA, dim(dat99)[1], length(predictor_vars))

for (i in 1:length(predictor_vars)){
  pred_data[,i]<- find_colvar(predictor_vars[i])
}

final_pred_data <- data.frame(pred_data)
names(final_pred_data) <- c("A12_var", "B15_var", "C20_var", "C22_var", "B9_var", "B12_var", "G9_var")

corrgram(final_pred_data)

```


Analysis Part 2 on Comments
```{r}
model_data <-cbind(comments, final_pred_data)
model <- glm(data= model_data, comments~. , family = "binomial")
plot(model)
summary(model)
corrgram(model_data)
```


Extreme Values in B1 and B3?

Social Change Variables
```{r}
data<- data %>% mutate(change_alc_pol = as.numeric(B5 == 2 | B5 == 3) )
data<- data %>% mutate(min_drink_age = as.numeric(B13 != 5 ))
data<- data %>% mutate(agree_alc_pol = as.numeric(B4 == 3 | B4 == 4) )
data<- data %>% mutate(change_tob_pol = as.numeric(B16 != 4 & B17 != 4 & B17 != B16) )
```


Create Final Model Data Set
```{r}
final_model_data <- cbind(model_data, data[,457:460])
corrgram(final_model_data)
```


Model Gradient Variances as predictors of Social Change Variables
```{r}

#CHANGE ALC POLICY

# Importance Variables
model <- glm(data= final_model_data, change_alc_pol~ A12_var+  B15_var + C20_var + C22_var , family = "binomial")
summary(model)

#Importance and Like Variables
model <- glm(data= final_model_data, change_alc_pol~ A12_var+  B15_var + C20_var + C22_var + B9_var + B12_var + G9_var , family = "binomial")
summary(model)

#AGREE ALC POLICY

# Importance Variables
model <- glm(data= final_model_data, agree_alc_pol~ A12_var+  B15_var + C20_var + C22_var , family = "binomial")
summary(model)

#Importance and Like Variables
model <- glm(data= final_model_data, agree_alc_pol~ A12_var+  B15_var + C20_var + C22_var + B9_var + B12_var + G9_var , family = "binomial")
summary(model)


#MINIMUM DRINKING AGE

#Importance Variables
model <- glm(data= final_model_data, min_drink_age~ A12_var+  B15_var + C20_var + C22_var , family = "binomial")
summary(model)

#Importance and Like Variables
model <- glm(data= final_model_data, agree_alc_pol~ A12_var+  B15_var + C20_var + C22_var + B9_var + B12_var + G9_var , family = "binomial")
summary(model)


#CHANGE TOBACCO POLICY

#Importance Variables
model <- glm(data= final_model_data, change_tob_pol~ A12_var+  B15_var + C20_var + C22_var , family = "binomial")
summary(model)

#Importance and Like Variables
model <- glm(data= final_model_data, change_tob_pol~ A12_var+  B15_var + C20_var + C22_var + B9_var + B12_var + G9_var , family = "binomial")
summary(model)
```


Multicollinearity (maybe check some more)

```{r}
corrgram(final_pred_data)
summary(lm(data= final_pred_data, C22_var ~.))
```

Sparse PCA
```{r}
#install.packages("sparsepca")
require(sparsepca)
#pca <- robspca(final_pred_data)
#summary(pca)
```

Extract School Policy Variables and Drink/Tobacco Usage

```{r}
#Tobacco and Drinking Policy
data <- data %>% mutate(school_alc_pol = as.factor(B2)) %>% mutate(stren_alc_pol = as.numeric(B3 == 1 | B3 == 3)) %>% mutate(school_tob_pol = as.factor(B16))
  
#Drinking
data <- data %>% mutate(drinks_occasions = ifelse(is.na(C9), 0, C9)) %>% mutate(drinks_num = ifelse(is.na(C10), 0, C10))

#Tobacco Usage
data <- data %>% mutate(smoking_num = ifelse(is.na(E3), 0, E3)) %>% mutate(smoking_occasions = ifelse(is.na(E5), 0, E5))

final_model_data <- cbind(final_model_data,data[,461:467])
```

Regress Engagement on School Policy and Personal Behavior
```{r}
#Add Means
data <- data %>% mutate(B15_mean = rowMeans(data %>% select(starts_with("B15"))))
final_model_data <- final_model_data %>% mutate(B15_mean = rowMeans(data %>% select(starts_with("B15"))))
data <- data %>% mutate(A12_mean = rowMeans(data %>% select(starts_with("A12"))))
final_model_data <- final_model_data %>% mutate(A12_mean = rowMeans(data %>% select(starts_with("A12"))))
data <- data %>% mutate(C20_mean = rowMeans(data %>% select(starts_with("C20"))))
final_model_data <- final_model_data %>% mutate(C20_mean = rowMeans(data %>% select(starts_with("C20"))))
data <- data %>% mutate(C22_mean = rowMeans(data %>% select(starts_with("C22"))))
final_model_data <- final_model_data %>% mutate(C22_mean = rowMeans(data %>% select(starts_with("C22"))))

summary(lm(data = final_model_data, A12_var ~ school_alc_pol + stren_alc_pol + school_tob_pol + drinks_occasions + drinks_num + smoking_num + smoking_occasions))

summary(lm(data = final_model_data, B15_var ~ school_alc_pol + stren_alc_pol + school_tob_pol + drinks_occasions + drinks_num + smoking_num + smoking_occasions))

summary(lm(data = final_model_data, C20_var ~ school_alc_pol + stren_alc_pol + school_tob_pol + drinks_occasions + drinks_num + smoking_num + smoking_occasions))

summary(lm(data = final_model_data, C22_var ~ school_alc_pol + stren_alc_pol + school_tob_pol + drinks_occasions + drinks_num + smoking_num + smoking_occasions))
```

Regress Social Change on Engagement and Person Behavior (with B15_var and B15_mean)
```{r}

summary(glm(data = final_model_data, change_alc_pol ~ A12_var + A12_mean +B15_mean +  B15_var + C20_var + C20_mean + C22_var + C22_mean + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, change_tob_pol ~ A12_var + A12_mean +B15_mean +  B15_var + C20_var + C20_mean + C22_var + C22_mean + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, agree_alc_pol ~ A12_var + A12_mean +B15_mean +  B15_var + C20_var + C20_mean + C22_var + C22_mean + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, min_drink_age ~ A12_var + A12_mean +B15_mean +  B15_var + C20_var + C20_mean + C22_var + C22_mean + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))
```


Regress Social Change on Engagement and Person Behavior (without B15_var and B15_mean)
```{r}

summary(glm(data = final_model_data, change_alc_pol ~ A12_var + C20_var + C22_var + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, change_tob_pol ~ A12_var + C20_var + C22_var + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, agree_alc_pol ~ A12_var + C20_var + C22_var + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))

summary(glm(data = final_model_data, min_drink_age ~ A12_var + C20_var + C22_var + school_alc_pol + stren_alc_pol + school_tob_pol  + drinks_occasions + drinks_num + smoking_num + smoking_occasions, family = "binomial"))
```

Social Engagement Variables and Perception Variable (not sure what to do with this variable, but could be cool)

```{r}
data <- data %>% mutate(advice = D4) %>% mutate(complaint = D5) %>% mutate(perception = D3B/D3A)
final_model_data <- final_model_data %>% mutate(advice = data$D4) %>% mutate(complaint = data$D5) %>% mutate(perception = data$D3B/data$D3A)
hist(final_model_data$perception)
summary(lm(perception ~ . , data = final_model_data))
#plot(lm(perception ~ . , data = final_model_data))
```

```{r}
corrgram(final_model_data)
final_model_data
```



Factor Model?