---
title: "Data Exploration"
author: "Irene Ji"
date: "2/6/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(purrr)
library(tidyr)
library(ggplot2)
library(cowplot)
library(corrplot)
library(tidyverse)
```

```{r}
load("dat.RData")
```

```{r}
dat93_Recode <- dat93[,284:405]
apply(dat93_Recode, 2, function(x) unique(x))

dat93_Recode[,1:10] %>%
  keep(is.numeric) %>% 
  gather() %>% 
  ggplot(aes(value)) +
    facet_wrap(~ key, scales = "free") +
    geom_histogram()
```

Most columns have binary responses, and they are reflecting some aspects of drinking/ smoking/ drug use behaviours. How to select response variable is a problem...


### Use drinkcat for binge drink (CAS Study)
the term binge is referring to the consumption of five drinks in a row for males or four drinks in a row for females on a single occasion within a 2-week time period
```{r}
p1 <- ggplot(dat93,aes(x = DRINKCAT)) + geom_histogram() + ggtitle("93")
p2 <- ggplot(dat97,aes(x = DRINKCAT)) + geom_histogram() + ggtitle("97")
p3 <- ggplot(dat99,aes(x = DRINKCAT)) + geom_histogram() + ggtitle("99")
p4 <- ggplot(dat01,aes(x = DRINKCAT)) + geom_histogram() + ggtitle("01")

plot_grid(p1,p2,p3,p4)
```
Binge drink levels do not seem to differ much across years.  


### Drug use in 30 days / 1 year (E1)
```{r}
dat93[1,]
Druguse_93 <- dat93[,names(dat93) %in% c("DAYE1A","DAYE1B","DAYE1C","DAYE1D","DAYE1E","DAYE1F",
                                 "DAYE1G","DAYE1H","DAYE1I","DAYE1J","DAYE1K","DAYE1L",
                                 "DAYE1M","YEARE1A","YEARE1B","YEARE1C","YEARE1D","YEARE1E","YEARE1F",
                                 "YEARE1G","YEARE1H","YEARE1I","YEARE1J","YEARE1K","YEARE1L",
                                 "YEARE1M")]
# sum them up
Druguse_93 <- Druguse_93 %>% mutate(total_day = DAYE1A + DAYE1B + DAYE1C + DAYE1D +
                                          DAYE1E + DAYE1F + DAYE1G + DAYE1H + DAYE1I +
                                          DAYE1J + DAYE1K + DAYE1L + DAYE1M,
                                    total_year = YEARE1A + YEARE1B + YEARE1C + YEARE1D +
                                          YEARE1E + YEARE1F + YEARE1G + YEARE1H + YEARE1I + 
                                          YEARE1J + YEARE1K + YEARE1L + YEARE1M)
Druguse_93 <- Druguse_93[complete.cases(Druguse_93),]
corrplot(cor(Druguse_93))

p1 <- ggplot(Druguse_93,aes(x = total_day)) + geom_histogram()
p2 <- ggplot(Druguse_93,aes(x = total_year)) + geom_histogram()
plot_grid(p1,p2)
```
### Variance study
```{r}
policy_opinion_93 <- dat93[,grepl("B\\d+", names(dat93))]
# names(policy_opinion_93)
policy_opinion_93 <- policy_opinion_93[,-ncol(policy_opinion_93)]
var <- apply(policy_opinion_93,1,function(x) var(x, na.rm = TRUE))
hist(var)
```


